Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Simple spell check.

\begin{table}
	\centering
	\caption{The number of disagreed online clone pair condidates before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filters} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filters} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{Filters*: \textit{L}=clone line $\geq 10$, \textit{S}=similarity $\geq 85\%$,}  \\
		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
	\end{tabular} %
	%}
\end{table}

@@

Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}. Our study adopted on of the patterns into our online code cloning patterns.

>>>>

\begin{table}
	\centering
	\caption{The number of disagreed online clone pair candidates before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filters} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filters} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{Filters*: \textit{L}=clone line $\geq 10$, \textit{S}=similarity $\geq 85\%$,}  \\
		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
	\end{tabular} %
	%}
\end{table}

@@

Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}. Our study adopted on of the patterns into our online code cloning patterns.
